The \emph{FThresholds} package for \emph{Macaulay2}

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Edits to Section 3 of the FThresholds paper

Consider the following example which has $F$-pure threshold equal to {1/2}, see \cite[Example 4.3]{MustataYoshidaTestIdealVsMultiplierIdeals}.
\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i1 : loadPackage "FThresholds"

@@

The command {\tt isFJumpingExponent} is implemented similarly, a value $t$ is an $F$-jumping exponent if and only if
\[
\tau(R, f^t) \neq \tau(R, f^{t-\epsilon}).
\]
Again, this command works as long as $R$ is $\bQ$-Gorenstein with index not divisible by $p$.

>>>>

Consider the following example.  Here, the $F$-pure threshold of $f$ equals to $1/2$; see \cite[Example 4.3]{MustataYoshidaTestIdealVsMultiplierIdeals}.
\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i1 : loadPackage "FThresholds"

@@

The function {\tt isFJumpingExponent} is implemented in a similar way, using the fact that a value $t$ is an $F$-jumping exponent if and only if the test ideals 
$\tau(R, f^t)$ and $\tau(R, f^{t-\epsilon})$ differ. 
Again, this command is implemented in rings that are $\bQ$-Gorenstein with index not divisible by $p$.
